### 2016-02-14 README.Rmd
misc
misc
more things that I forgot to fix!

`v- is_miss` visualises the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss` is similar to `missing.pattern.plot` from the `mi` package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (well, at 14/02/2016).

@@

The classes are represented on the legend, and missing data represented by grey. This tells us

@@

`vis_datly`. `vis_dat` could include an interactive version of the plots (similar to csv-fingerprint), so that you can

# Thank yous

Thank you to @jennbc, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about this, and for her code contributions.

@@

# Known Issues.

**Individual cells do not have an individual class**
Due to the fact that R coerces a vector to be the same type, this means that you cannot have something like c("a", 1L, 10.555) together as a vector, as it will just convert this to `[1] "a"      "1"      "10.555"`. This means that you don't get the ideal feature of picking up on nuances such as individuals cells that are different classes in the dataframe. Perhaps there is a way to read in a csv as a list so that these features are preserved?

**Missing Data not listed in legend**

When running the example below, the gray bars indicate missing values, but these are currently not specified as missing values.

>>>>

- `vis_miss` visualises the missing data, and allows for missingness to be clustered and columns rearranged. `vis_miss` is similar to `missing.pattern.plot` from the `mi` package. Unfortunately `missing.pattern.plot` is no longer in the `mi` package (well, at 14/02/2016).

@@

The classes are represented on the legend, and missing data represented by grey. This tells us that R reads this dataset as having numeric and integer values, along with some missing data in `Ozone` and `Solar.R`.

@@

`vis_datly`. `vis_dat` could include an interactive version of the plots using `plotly`, so that you can actually _see_ what is inside the data.

# Thank you

Thank you to Jenny Bryan, whose [tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me thinking about vis_dat, and for her code contributions.

@@
